Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-09 exp1/iswc2013.tex
cosmetics
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@550 43ef1190-90fd-4dd7-a769-d0121f02b80e

The main objective of this paper is not to establish that the
optimization is significant, it is merely a simulation. It is to
establish a critical practice of evaluations. It is of critical
importance that we understand why some effects are critical.\todo{add
  table of effects} That
``Implement'' is significant is hardly a surprise, that is what we
worked for. That the main effects ``Union'', ``Optional'' and ``Lang''
are strong is also due to that these are fairly demanding things to
evaluate. Since the delay we inserted affects all kinds of joins, it
is also intuitive that interactions between ``Implement'' and those
that require joins are strong. The strong ``BGPComp:Lang'' and
``Lang:Union'' interactions might be due to that the many more triples
needs to be searched for a language tag in one case. However, the
positive ``Implement:TripleC'' interaction evades such explanations;
in fact, it hints that our optimization may not work as well for
larger databases. This is a clear indication that the separation
between levels for the sizes of the data-set is too small and should
be investigated further. Such reasoning should be applied to all
significant effects.

@@

Kjetil Kjernsmo would like to thank his main supervisor Martin Giese
for kind assistance in writing this paper. He would also like to
thank Steve Harris for his generous support in degrading his excellent
work on 4store.

>>>>

The main objective of this paper is not to establish that the
optimization is significant, it is merely a simulation. It is to
establish a critical practice of evaluations. It is of critical
importance that we understand why some effects are
significant.\todo{add table of effects} That ``Implement'' is
significant is hardly a surprise, that is what we worked for. That the
main effects ``Union'', ``Optional'' and ``Lang'' are strong is also
due to that these are fairly demanding things to evaluate. Since the
delay we inserted affects all kinds of joins, it is also intuitive
that interactions between ``Implement'' and those that require joins
are strong. The strong ``BGPComp:Lang'' and ``Lang:Union''
interactions might be due to that the many more triples needs to be
searched for a language tag in one case. However, the positive
``Implement:TripleC'' interaction evades such explanations; in fact,
it hints that our optimization may not work as well for larger
databases. This is a clear indication that the separation between
levels for the sizes of the data-set is too small and should be
investigated further. Such reasoning should be applied to all
significant effects.

@@

Kjetil Kjernsmo would like to thank his main supervisor Martin Giese
for kind assistance. He would also like to
thank Steve Harris for his generous support in degrading his excellent
work on 4store.
